Raw Data Comparison

### 2019-09-10 Raw Data Comparison.Rmd
...

But what if I, as a quick test, normalize the validation cohort with itself? This looks better here, but when I use this for predictions it doesn't significantly change the results.

@@

@@

wt.sds = sapply(sds, function(x) weighted.mean(x,global.sd,w=c(0.2)))

>>>>

## Normalize Validation to itself

Instead scaling using z-values from the trianing data, I can do it from within the validation cohort. This looks better here, but when I use this for predictions it doesn't significantly change the results.

@@

### Predictions
```{r}
preds = do.call(bind_rows, purrr::map(
  list.files('~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf/predictions_scale_within_cohort/0.9/', pattern='predictions.tsv', recursive = T, full.names = T), 
  function(f) read_tsv(f, col_types = 'cddcccccccc'))) %>% mutate(Endoscopy = as.Date(Endoscopy)) %>% dplyr::select(-`Path Notes`)

@@

wt.sds = sapply(sds, function(x) weighted.mean(c(x,global.sd),w=c(0.5,0.5)))
